### 2023-10-25 journal/related.tex
update to related work

\paragraph{Array-Based Queues.}
Arrays can be used to implement queues with bounded capacity \cite{DBLP:conf/iceccs/ColvinG05,DBLP:conf/icdcn/Shafiei09,DBLP:conf/spaa/TsigasZ01}.  
%Similar to the front and back pointers of list-based queues, indices
Dequeues and enqueues update
indices of the front and back elements using CAS instructions.
Gidenstam, Sundell, and Tsigas~\cite{DBLP:conf/opodis/GidenstamST10} avoid
the capacity constraint by using a linked list of arrays.
These solutions also use $\Omega(p)$ steps per operation due to the CAS retry problem.

@@

>>>>

\paragraph{Array-Based Queues.}
Arrays can be used to implement queues with bounded capacity \cite{DBLP:conf/iceccs/ColvinG05,PMG16,DBLP:conf/icdcn/Shafiei09,DBLP:conf/spaa/TsigasZ01}.  
%Similar to the front and back pointers of list-based queues, indices
Dequeues and enqueues update
indices of the front and back elements using CAS instructions.
Gidenstam, Sundell, and Tsigas~\cite{DBLP:conf/opodis/GidenstamST10} avoid
the capacity constraint by using a linked list of arrays.
These solutions also use $\Omega(p)$ steps per operation due to the CAS retry problem.

@@

\here{Maybe mention experimental work of \cite{KLM+23} here or in intro}
